---
format: dashboard
logo: "https://static-00.iconduck.com/assets.00/strava-icon-512x512-47ehfaer.png"
theme: 
  - darkly
  - styles.scss
expandable: false
---

```{r load-packages}
library(dplyr)
library(jsonlite)
library(httr)
library(ggplot2)
library(stringr)
library(tidyr)
library(purrr)
library(lubridate)
library(leaflet)
library(DT)
library(plotly)
```

```{r load-data}
load("stravawattz.RData")
```

# STRAVAWATTZ

## Column

### Window 1

{{< inadsense >}}

### Window 2

plot(1,2)

### Window 3

plot(1,2)

### Window 4

plot(1,2)

# Running

## Row {height="20%"}

### Column {width="15%"}

```{r running-box-sessions}
#| content: valuebox
list(
  title = paste("In", format(Sys.Date(), '%Y')),
  #icon = "hash",
  color = "success",
  value = paste0(length(df_running_365$id), " sessions")
)
```

### Column {width="85%"}

```{r running-plot-calendar}
#| padding: 0px
plot_calendar_running
```

## Row {height="80%"}

### Column {width="15%"}

#### Row {height="25%"}

```{r running-box-distance}
#| content: valuebox
#| title: "Total Distance"
list(
  #icon = "rocket-takeoff-fill",
  color = "success",
  value = paste0(round(sum(df_running_365$distance, na.rm = TRUE) / 1000, 0), "km")
)
```

#### Row {height="25%"}

```{r running-box-time}
#| content: valuebox
#| title: "Total Duration"
#| padding: 0px
list(
  #icon = "speedometer",
  color = "success",
  value = ifelse(sum(df_running_365$time, na.rm = TRUE) / 60 >= 300, paste0(round(floor(sum(df_running_365$time, na.rm = TRUE) / 60 / 60), 0),"h", ifelse(round(((sum(df_running_365$time, na.rm = TRUE) / 60 / 60) - floor(sum(df_running_365$time, na.rm = TRUE) / 60 / 60)) * 60, 0)<10,paste0("0",round(((sum(df_running_365$time, na.rm = TRUE) / 60 / 60) - floor(sum(df_running_365$time, na.rm = TRUE) / 60 / 60)) * 60, 0)),round(((sum(df_running_365$time, na.rm = TRUE) / 60 / 60) - floor(sum(df_running_365$time, na.rm = TRUE) / 60 / 60)) * 60, 0)), "min"), paste0(round(sum(df_running_365$time, na.rm = TRUE) / 60, 0), "min"))
)
```

#### Row {height="25%"}

```{r running-box-pace}
#| content: valuebox
#| title: "Average Pace"
list(
  #icon = "speedometer",
  color = "success",
  value = ifelse(is.nan(as.numeric(floor(pace <- sum(df_running_365$distance * df_running_365$pace) / sum(df_running_365$distance)), ":", round((pace %% 1) * 60))), "No data",paste0(floor(pace <- sum(df_running_365$distance * df_running_365$pace) / sum(df_running_365$distance)), ":", round((pace %% 1) * 60), "/km"))
)
```

#### Row {height="25%"}

```{r running-box-hr}
#| content: valuebox
#| title: "Average HR"
list(
  #icon = "speedometer",
  color = "success",
  value = ifelse(is.nan(as.numeric(round(sum(df_running_365$speed * df_running_365$hr) / sum(df_running_365$speed), 0))), "No data", paste0(round(sum(df_running_365$speed * df_running_365$hr) / sum(df_running_365$speed), 0), "bpm"))
)
```

### Column {width="85%"}

#### Row {height="100%"}

##### Column {.tabset title="Rankings" width="50%"}

```{r}
#| padding: 0px
#| title: "Distance"
plot_distance_running
```

```{r}
#| padding: 0px
#| title: "Time"
plot_time_running
```

```{r}
#| padding: 0px
#| title: "Pace"
plot_pace_running
```

```{r}
#| padding: 0px
#| title: "HR"
plot_hr_running
```

##### Column {width="50%"}

###### Row {.tabset title="Maps"}

```{r}
#| title: "Latest"
#| padding: 0px 
plot_map1_running
```

```{r}
#| title: "Fastest"
#| padding: 0px 
plot_map2_running
```

```{r}
#| title: "Longest"
#| padding: 0px 
plot_map3_running
```

# Cycling

## Row {height="20%"}

### Column {width="15%"}

```{r cycling-box-sessions}
#| content: valuebox
list(
  title = paste("In", format(Sys.Date(), '%Y')),
  #icon = "hash",
  color = "warning",
  value = paste0(length(df_cycling_365$id), " sessions")
)
```

### Column {width="85%"}

```{r cycling-plot-calendar}
#| padding: 0px
plot_calendar_cycling
```

## Row {height="80%"}

### Column {width="15%"}

#### Row {height="25%"}

```{r cycling-box-distance}
#| content: valuebox
#| title: "Total Distance"
list(
  #icon = "rocket-takeoff-fill",
  color = "warning",
  value = paste0(round(sum(df_cycling_365$distance, na.rm = TRUE) / 1000, 0), "km")
)
```

#### Row {height="25%"}

```{r cycling-box-time}
#| content: valuebox
#| title: "Total Duration"
#| padding: 0px
list(
  #icon = "speedometer",
  color = "warning",
  value = ifelse(sum(df_cycling_365$time, na.rm = TRUE) / 60 >= 300, paste0(round(floor(sum(df_cycling_365$time, na.rm = TRUE) / 60 / 60), 0),"h", ifelse(round(((sum(df_cycling_365$time, na.rm = TRUE) / 60 / 60) - floor(sum(df_cycling_365$time, na.rm = TRUE) / 60 / 60)) * 60, 0)<10,paste0("0",round(((sum(df_cycling_365$time, na.rm = TRUE) / 60 / 60) - floor(sum(df_cycling_365$time, na.rm = TRUE) / 60 / 60)) * 60, 0)),round(((sum(df_cycling_365$time, na.rm = TRUE) / 60 / 60) - floor(sum(df_cycling_365$time, na.rm = TRUE) / 60 / 60)) * 60, 0)), "min"), paste0(round(sum(df_cycling_365$time, na.rm = TRUE) / 60, 0), "min"))
)
```

#### Row {height="25%"}

```{r cycling-box-pace}
#| content: valuebox
#| title: "Average Speed"
list(
  #icon = "speedometer",
  color = "warning",
  value = ifelse(is.nan(as.numeric(round(sum(df_cycling_365$distance * df_cycling_365$speed) / sum(df_cycling_365$distance), 1))), "No data", paste0(round(sum(df_cycling_365$distance * df_cycling_365$speed) / sum(df_cycling_365$distance), 1), "km/h"))
)
```

#### Row {height="25%"}

```{r cycling-box-hr}
#| content: valuebox
#| title: "Average HR"
list(
  #icon = "speedometer",
  color = "warning",
  value = ifelse(is.na(as.numeric(round(sum(df_cycling_365$speed * df_cycling_365$hr) / sum(df_cycling_365$speed), 0))), "No data", paste0(round(sum(df_cycling_365$speed * df_cycling_365$hr) / sum(df_cycling_365$speed), 0), "bpm"))
)
```

### Column {width="85%"}

#### Row {height="100%"}

##### Column {.tabset title="Rankings" width="50%"}

```{r}
#| padding: 0px
#| title: "Distance"
plot_distance_cycling
```

```{r}
#| padding: 0px
#| title: "Time"
plot_time_cycling
```

```{r}
#| padding: 0px
#| title: "Speed"
plot_pace_cycling
```

```{r}
#| padding: 0px
#| title: "HR"
plot_hr_cycling
```

##### Column {width="50%"}

###### Row {.tabset title="Maps"}

```{r}
#| title: "Latest"
#| padding: 0px 
plot_map1_cycling
```

```{r}
#| title: "Fastest"
#| padding: 0px 
plot_map2_cycling
```

```{r}
#| title: "Longest"
#| padding: 0px 
plot_map3_cycling
```

# Swimming

## Row {height="20%"}

### Column {width="15%"}

```{r swimming-box-sessions}
#| content: valuebox
list(
  title = paste("In", format(Sys.Date(), '%Y')),
  #icon = "hash",
  color = "info",
  value = paste0(length(df_swimming_365$id), " sessions")
)
```

### Column {width="85%"}

```{r swimming-plot-calendar}
#| padding: 0px
plot_calendar_swimming
```

## Row {height="80%"}

### Column {width="15%"}

#### Row {height="25%"}

```{r swimming-box-distance}
#| content: valuebox
#| title: "Total Distance"
list(
  #icon = "rocket-takeoff-fill",
  color = "info",
  value = paste0(round(sum(df_swimming_365$distance, na.rm = TRUE) / 1000, 0), "km")
)
```

#### Row {height="25%"}

```{r swimming-box-time}
#| content: valuebox
#| title: "Total Duration"
#| padding: 0px
list(
  #icon = "speedometer",
  color = "info",
  value = ifelse(sum(df_swimming_365$time, na.rm = TRUE) / 60 >= 300, paste0(round(floor(sum(df_swimming_365$time, na.rm = TRUE) / 60 / 60), 0),"h", ifelse(round(((sum(df_swimming_365$time, na.rm = TRUE) / 60 / 60) - floor(sum(df_swimming_365$time, na.rm = TRUE) / 60 / 60)) * 60, 0)<10,paste0("0",round(((sum(df_swimming_365$time, na.rm = TRUE) / 60 / 60) - floor(sum(df_swimming_365$time, na.rm = TRUE) / 60 / 60)) * 60, 0)),round(((sum(df_swimming_365$time, na.rm = TRUE) / 60 / 60) - floor(sum(df_swimming_365$time, na.rm = TRUE) / 60 / 60)) * 60, 0)), "min"), paste0(round(sum(df_swimming_365$time, na.rm = TRUE) / 60, 0), "min"))
)
```

#### Row {height="25%"}

```{r swimming-box-pace}
#| content: valuebox
#| title: "Average Pace"
list(
  #icon = "speedometer",
  color = "info",
  value = ifelse(is.nan(as.numeric(floor(pace <- sum(df_swimming_365$distance * df_swimming_365$pace) / sum(df_swimming_365$distance)/10), ":", round((pace %% 1) * 60))), "No data", paste0(floor(pace <- sum(df_swimming_365$distance * df_swimming_365$pace) / sum(df_swimming_365$distance)/10), ":", round((pace %% 1) * 60), "/km"))
)
```

#### Row {height="25%"}

```{r swimming-box-hr}
#| content: valuebox
#| title: "Average HR"
list(
  #icon = "speedometer",
  color = "info",
  value = ifelse(is.nan(as.numeric(round(sum(df_swimming_365$speed * df_swimming_365$hr) / sum(df_swimming_365$speed), 0))), "No data", paste0(round(sum(df_swimming_365$speed * df_swimming_365$hr) / sum(df_swimming_365$speed), 0), "bpm"))
)
```

### Column {width="85%"}

#### Row {height="100%"}

##### Column {.tabset title="Rankings" width="50%"}

```{r}
#| padding: 0px
#| title: "Distance"
plot_distance_swimming
```

```{r}
#| padding: 0px
#| title: "Time"
plot_time_swimming
```

```{r}
#| padding: 0px
#| title: "Pace"
plot_pace_swimming
```

```{r}
#| padding: 0px
#| title: "HR"
plot_hr_swimming
```

##### Column {width="50%"}

###### Row {.tabset title="Maps"}

```{r}
#| title: "Latest"
#| padding: 0px 
plot_map1_swimming
```

```{r}
#| title: "Fastest"
#| padding: 0px 
plot_map2_swimming
```

```{r}
#| title: "Longest"
#| padding: 0px 
plot_map3_swimming
```

# Datasets

## Row {height="10%"}

### Column

::: {style="text-align: center; font-size: 20px; font-weight: bold; margin-bottom: 10px;"}
Running (all-time)
:::

### Column

::: {style="text-align: center; font-size: 20px; font-weight: bold; margin-bottom: 10px;"}
Cycling (all-time)
:::

### Column

::: {style="text-align: center; font-size: 20px; font-weight: bold; margin-bottom: 10px;"}
Swimming (all-time)
:::

## Row {height="90%"}

### Column {width="33%"}

```{r}
#| padding: 0px
datatable(df_running_all |> arrange(desc(date)) |> mutate(pace = sprintf("%02d:%02d", floor(pace), round((pace %% 1) * 60)), time = round(time/60,0), date = format(as.Date(date), "%y-%m-%d"), distance = format(round(distance/1000,1),1)) |> select(date, km = distance, time, pace, hr), rownames = FALSE, options = list(initComplete = JS("function(settings, json) {$(this.api().table().header()).css({'color': '#00bc8c', 'text-align': 'center', 'font-weight': 'bold'});}"), searching = FALSE, lengthChange = FALSE, pageLength = nrow(df_running_all), info = FALSE, columnDefs = list(list(className = 'dt-center', targets = 0:4)))) |>
  formatStyle(c("date", "pace", "km", "time", "hr"), color = "black", background = "#00bc8c")
```

### Column {width="33%"}

```{r}
#| padding: 0px
datatable(df_cycling_all |> arrange(desc(date)) |> mutate(speed = round(speed, 2), time = round(time/60,0), date = format(as.Date(date), "%y-%m-%d"), distance = format(round(distance/1000,1),1)) |> select(date, km = distance, time, speed, hr), rownames = FALSE, options = list(initComplete = JS("function(settings, json) {$(this.api().table().header()).css({'color': '#f39c12', 'text-align': 'center', 'font-weight': 'bold'});}"), searching = FALSE, lengthChange = FALSE, pageLength = nrow(df_cycling_all), info = FALSE, columnDefs = list(list(className = 'dt-center', targets = 0:4)))) |>
  formatStyle(c("date", "speed", "km", "time", "hr"), color = "black", background = "#f39c12")
```

### Column {width="33%"}

```{r}
#| padding: 0px
#| 
datatable(df_swimming_all |> arrange(desc(date)) |> mutate(pace = pace/10, pace = sprintf("%02d:%02d", floor(pace), round((pace %% 1) * 60)), time = round(time/60,0), date = format(as.Date(date), "%y-%m-%d"), distance = format(round(distance,1),1)) |> select(date, meter = distance, time, pace, hr), rownames = FALSE, options = list(initComplete = JS("function(settings, json) {$(this.api().table().header()).css({'color': '#3498db', 'text-align': 'center', 'font-weight': 'bold'});}"), searching = FALSE, lengthChange = FALSE, pageLength = nrow(df_swimming_all), info = FALSE, columnDefs = list(list(className = 'dt-center', targets = 0:4)))) |>
  formatStyle(c("date", "pace", "meter", "time", "hr"), color = "black", background = "#3498db")
```
