---
format: dashboard
title: STRAVAWATTZ
logo: Stravawattz.png
theme: 
  - darkly
  - styles.scss
expandable: false
---

```{r load-packages}
library(dplyr)
library(jsonlite)
library(httr)
library(ggplot2)
library(stringr)
library(tidyr)
library(purrr)
library(lubridate)
library(leaflet)
library(DT)
library(plotly)
library(openmeteo)
library(RColorBrewer)
```

```{r load-data}
load("stravawattz.RData")
```

# Home

## Row {height="100%"}

### Column {width="85%"}

#### Row {height="20%"}

##### Column {width="20%"}

```{r}
#| content: valuebox
list(
  title = "Running in 2025",
  #icon = "hash",
  color = "success",
  value = paste0(length(df_running_2025$id), " sessions")
)
```

##### Column {width="20%"}

```{r}
#| content: valuebox
list(
  title = "Cycling in 2025",
  #icon = "hash",
  color = "warning",
  value = paste0(length(df_cycling_2025$id), " sessions")
)
```

##### Column {width="20%"}

```{r}
#| content: valuebox
list(
  title = "Swimming in 2025",
  #icon = "hash",
  color = "info",
  value = paste0(length(df_swimming_2025$id), " sessions")
)
```

##### Column {width="40%"}

```{r}
plot_calendar_frontpage_2025
```

#### Row {height="80%"}

```{r}
plot_training_load
```

### Column {width="15%"}

#### Row {height="21%"}

```{r}
#| content: valuebox
list(
  title = "Training Load",
  #icon = "hash",
  # color = ifelse(status_today %in% c("Recovery", "Light"), "warning", ifelse(status_today == "Optimal", "primary", "danger")),
  color = "dark",
  value = status_today
)
```

#### Row {height="26.5%"}

```{r}
ATL_gauge
```

#### Row {height="26.5%"}

```{r}
CTL_gauge
```

#### Row {height="26.5%"}

```{r}
ACWR_gauge
```












# Running

## Row {height="100%"}

### Column {width="15%"}

#### Row {height="20%"}

```{r running-box-sessions}
#| content: valuebox
list(
  title = paste("Running in", format(Sys.Date(), '%Y')),
  #icon = "hash",
  color = "success",
  value = paste0(length(df_running_365$id), " sessions")
)
```

#### Row {height="20%"}

```{r running-box-distance}
#| content: valuebox
#| title: "Total Distance"
list(
  #icon = "rocket-takeoff-fill",
  color = "success",
  value = paste0(round(sum(df_running_365$distance, na.rm = TRUE) / 1000, 1), " km")
)
```

#### Row {height="20%"}

```{r running-box-time}
#| content: valuebox
#| title: "Total Duration"
#| padding: 0px
list(
  #icon = "speedometer",
  color = "success",
  value = ifelse(sum(df_running_365$time, na.rm = TRUE) / 60 >= 300, paste0(round(floor(sum(df_running_365$time, na.rm = TRUE) / 60 / 60), 0),"h ", ifelse(round(((sum(df_running_365$time, na.rm = TRUE) / 60 / 60) - floor(sum(df_running_365$time, na.rm = TRUE) / 60 / 60)) * 60, 0)<10,paste0("0",round(((sum(df_running_365$time, na.rm = TRUE) / 60 / 60) - floor(sum(df_running_365$time, na.rm = TRUE) / 60 / 60)) * 60, 0)),round(((sum(df_running_365$time, na.rm = TRUE) / 60 / 60) - floor(sum(df_running_365$time, na.rm = TRUE) / 60 / 60)) * 60, 0)), "min"), paste0(round(sum(df_running_365$time, na.rm = TRUE) / 60, 0), "min"))
)
```

#### Row {height="20%"}

```{r running-box-elevation}
#| content: valuebox
#| title: "Total Elevation"
list(
  #icon = "speedometer",
  color = "success",
  value = ifelse(sum(df_running_365$elevation, na.rm = TRUE) < 1000, paste0(round(sum(df_running_365$elevation, na.rm = TRUE), 1), " m"), paste0(round(sum(df_running_365$elevation, na.rm = TRUE)/1000, 1), " km"))
)
```

#### Row {height="20%"}

```{r running-box-cadence}
#| content: valuebox
#| title: "Average Cadence"
list(
  #icon = "rocket-takeoff-fill",
  color = "success",
  value = paste0("No data")
)
```

#### Row {height="20%"}

```{r running-box-pace}
#| content: valuebox
#| title: "Average Pace"
list(
  #icon = "speedometer",
  color = "success",
  value = ifelse(is.nan(as.numeric(floor(pace <- mean(df_running_365$pace, na.rm = TRUE)), ":", round((pace %% 1) * 60))), "No data",paste0(floor(pace <- mean(df_running_365$pace, na.rm = TRUE)), ":", ifelse(round((pace %% 1) * 60) < 10, paste0("0", round((pace %% 1) * 60)), round((pace %% 1) * 60)), "/km"))
)
```

#### Row {height="20%"}

```{r running-box-hr}
#| content: valuebox
#| title: "Average HR"
list(
  #icon = "speedometer",
  color = "success",
  value = ifelse(is.nan(as.numeric(round(sum(df_running_365$speed * df_running_365$hr) / sum(df_running_365$speed), 0))), "No data", paste0(round(sum(df_running_365$speed * df_running_365$hr) / sum(df_running_365$speed), 0), " bpm"))
)
```

### Column {width="42.5%"}

#### Row {height="25%"}

##### Column {.tabset title="Calendar"}

```{r}
#| padding: 0px
#| title: "Daily"
plot_calendar_running_d
```

```{r}
#| padding: 0px
#| title: "Monthly"
plot_calendar_running_m
```

#### Row {height="75%"}

##### Column {.tabset title="Rankings"}

```{r}
#| padding: 0px
#| title: "Distance"
plot_distance_running
```

```{r}
#| padding: 0px
#| title: "Time"
plot_time_running
```

```{r}
#| padding: 0px
#| title: "Elevation"
plot_elevation_running
```

```{r}
#| padding: 0px
#| title: "Pace"
plot_pace_running
```

```{r}
#| padding: 0px
#| title: "HR"
plot_hr_running
```

### Column {width="42.5%"}

#### Row {height="25%"}

##### Column {.tabset title="Cumulative"}

```{r}
#| padding: 0px
#| title: "Distance"
plot_cum_distance_running
```

```{r}
#| padding: 0px
#| title: "Time"
plot_cum_time_running
```

```{r}
#| padding: 0px
#| title: "Elevation"
plot_cum_elevation_running
```

#### Row {height="75%"}

##### Column {.tabset title="Maps"}

```{r}
#| title: "Latest"
#| padding: 0px 
plot_map1_running
```

```{r}
#| title: "Fastest"
#| padding: 0px 
plot_map2_running
```

```{r}
#| title: "Longest"
#| padding: 0px 
plot_map3_running
```

```{r}
#| title: "All"
#| padding: 0px 
plot_map4_running
```

# Cycling

## Row {height="100%"}

### Column {width="15%"}

#### Row {height="14.29%"}

```{r cycling-box-sessions}
#| content: valuebox
list(
  title = paste("Cycling in", format(Sys.Date(), '%Y')),
  #icon = "hash",
  color = "warning",
  value = paste0(length(df_cycling_365$id), " sessions")
)
```

#### Row {height="14.29%"}

```{r cycling-box-distance}
#| content: valuebox
#| title: "Total Distance"
list(
  #icon = "rocket-takeoff-fill",
  color = "warning",
  value = paste0(round(sum(df_cycling_365$distance, na.rm = TRUE) / 1000, 1), " km")
)
```

#### Row {height="14.29%"}

```{r cycling-box-time}
#| content: valuebox
#| title: "Total Duration"
#| padding: 0px
list(
  #icon = "speedometer",
  color = "warning",
  value = ifelse(sum(df_cycling_365$time, na.rm = TRUE) / 60 >= 300, paste0(round(floor(sum(df_cycling_365$time, na.rm = TRUE) / 60 / 60), 0),"h ", ifelse(round(((sum(df_cycling_365$time, na.rm = TRUE) / 60 / 60) - floor(sum(df_cycling_365$time, na.rm = TRUE) / 60 / 60)) * 60, 0)<10,paste0("0",round(((sum(df_cycling_365$time, na.rm = TRUE) / 60 / 60) - floor(sum(df_cycling_365$time, na.rm = TRUE) / 60 / 60)) * 60, 0)),round(((sum(df_cycling_365$time, na.rm = TRUE) / 60 / 60) - floor(sum(df_cycling_365$time, na.rm = TRUE) / 60 / 60)) * 60, 0)), "min"), paste0(round(sum(df_cycling_365$time, na.rm = TRUE) / 60, 0), "min"))
)
```

#### Row {height="14.29%"}

```{r cycling-box-elevation}
#| content: valuebox
#| title: "Total Elevation"
list(
  #icon = "speedometer",
  color = "warning",
  value = ifelse(sum(df_cycling_365$elevation, na.rm = TRUE) < 1000, paste0(round(sum(df_cycling_365$elevation, na.rm = TRUE), 1), " m"), paste0(round(sum(df_cycling_365$elevation, na.rm = TRUE)/1000, 1), " km"))
)
```

#### Row {height="14.29%"}

```{r cycling-box-cadence}
#| content: valuebox
#| title: "Average Cadence"
list(
  #icon = "speedometer",
  color = "warning",
  value = paste0(round(mean(df_cycling_365$cadence, na.rm = TRUE), 1), " rpm")
)
```

#### Row {height="14.29%"}

```{r cycling-box-pace}
#| content: valuebox
#| title: "Average Speed"
list(
  #icon = "speedometer",
  color = "warning",
  value = ifelse(is.nan(as.numeric(round(mean(df_cycling_365$speed, na.rm = TRUE), 1))), "No data", paste0(round(mean(df_cycling_365$speed, na.rm = TRUE), 1), " km/h"))
)
```

#### Row {height="14.29%"}

```{r cycling-box-hr}
#| content: valuebox
#| title: "Average HR"
list(
  #icon = "speedometer",
  color = "warning",
  value = ifelse(is.na(as.numeric(round(sum(df_cycling_365$speed * df_cycling_365$hr) / sum(df_cycling_365$speed), 0))), "No data", paste0(round(sum(df_cycling_365$speed * df_cycling_365$hr) / sum(df_cycling_365$speed), 0), " bpm"))
)
```

### Column {width="42.5%"}

#### Row {height="25%"}

##### Column {.tabset title="Calendar"}

```{r}
#| padding: 0px
#| title: "Daily"
plot_calendar_cycling_d
```

```{r}
#| padding: 0px
#| title: "Monthly"
plot_calendar_cycling_m
```

#### Row {height="75%"}

##### Column {.tabset title="Rankings"}

```{r}
#| padding: 0px
#| title: "Distance"
plot_distance_cycling
```

```{r}
#| padding: 0px
#| title: "Time"
plot_time_cycling
```

```{r}
#| padding: 0px
#| title: "Elevation"
plot_elevation_cycling
```

```{r}
#| padding: 0px
#| title: "Speed"
plot_pace_cycling
```

```{r}
#| padding: 0px
#| title: "HR"
plot_hr_cycling
```

### Column {width="42.5%"}

#### Row {height="25%"}

##### Column {.tabset title="Cumulative"}

```{r}
#| padding: 0px
#| title: "Distance"
plot_cum_distance_cycling
```

```{r}
#| padding: 0px
#| title: "Time"
plot_cum_time_cycling
```

```{r}
#| padding: 0px
#| title: "Elevation"
plot_cum_elevation_cycling
```

#### Row {height="75%"}

##### Column {.tabset title="Maps"}

```{r}
#| title: "Latest"
#| padding: 0px 
plot_map1_cycling
```

```{r}
#| title: "Fastest"
#| padding: 0px 
plot_map2_cycling
```

```{r}
#| title: "Longest"
#| padding: 0px 
plot_map3_cycling
```

```{r}
#| title: "All"
#| padding: 0px 
plot_map4_cycling
```

# Swimming

## Row {height="100%"}

### Column {width="15%"}

#### Row {height="20%"}

```{r swimming-box-sessions}
#| content: valuebox
list(
  title = paste("Swimming in", format(Sys.Date(), '%Y')),
  #icon = "hash",
  color = "info",
  value = paste0(length(df_swimming_365$id), " sessions")
)
```

#### Row {height="20%"}

```{r swimming-box-distance}
#| content: valuebox
#| title: "Total Distance"
list(
  #icon = "rocket-takeoff-fill",
  color = "info",
  value = paste0(round(sum(df_swimming_365$distance, na.rm = TRUE) / 1000, 1), " km")
)
```

#### Row {height="20%"}

```{r swimming-box-time}
#| content: valuebox
#| title: "Total Duration"
#| padding: 0px
list(
  #icon = "speedometer",
  color = "info",
  value = ifelse(sum(df_swimming_365$time, na.rm = TRUE) / 60 >= 300, paste0(round(floor(sum(df_swimming_365$time, na.rm = TRUE) / 60 / 60), 0),"h ", ifelse(round(((sum(df_swimming_365$time, na.rm = TRUE) / 60 / 60) - floor(sum(df_swimming_365$time, na.rm = TRUE) / 60 / 60)) * 60, 0)<10,paste0("0",round(((sum(df_swimming_365$time, na.rm = TRUE) / 60 / 60) - floor(sum(df_swimming_365$time, na.rm = TRUE) / 60 / 60)) * 60, 0)),round(((sum(df_swimming_365$time, na.rm = TRUE) / 60 / 60) - floor(sum(df_swimming_365$time, na.rm = TRUE) / 60 / 60)) * 60, 0)), "min"), paste0(round(sum(df_swimming_365$time, na.rm = TRUE) / 60, 0), "min"))
)
```

#### Row {height="20%"}

```{r swimming-box-lengths}
#| content: valuebox
#| title: "Total Lengths (50m)"
#| padding: 0px
list(
  #icon = "speedometer",
  color = "info",
  value = paste0(ifelse(sum(df_swimming_365$distance)/50%%2==0, sum(df_swimming_365$distance)/50, (sum(df_swimming_365$distance)/50)+1), " lengths")
)
```

#### Row {height="20%"}

```{r swimming-box-pace}
#| content: valuebox
#| title: "Average Pace"
list(
  #icon = "speedometer",
  color = "info",
  value = ifelse(is.nan(as.numeric(floor(pace <- mean(df_swimming_365$pace, na.rm = TRUE)/10), ":", round((pace %% 1) * 60))), "No data", paste0(floor(pace <- mean(df_swimming_365$pace, na.rm = TRUE)/10), ":", ifelse(round((pace %% 1) * 60) < 10, paste0("0", round((pace %% 1) * 60)), round((pace %% 1) * 60)), "/100m"))
)
```

#### Row {height="20%"}

```{r swimming-box-hr}
#| content: valuebox
#| title: "Average HR"
list(
  #icon = "speedometer",
  color = "info",
  value = ifelse(is.nan(as.numeric(round(sum(df_swimming_365$speed * df_swimming_365$hr) / sum(df_swimming_365$speed), 0))), "No data", paste0(round(sum(df_swimming_365$speed * df_swimming_365$hr) / sum(df_swimming_365$speed), 0), " bpm"))
)
```

### Column {width="42.5%"}

#### Row {height="25%"}

##### Column {.tabset title="Calendar"}

```{r}
#| padding: 0px
#| title: "Daily"
plot_calendar_swimming_d
```

```{r}
#| padding: 0px
#| title: "Monthly"
plot_calendar_swimming_m
```

#### Row {height="75%"}

##### Column {.tabset title="Rankings"}

```{r}
#| padding: 0px
#| title: "Distance"
plot_distance_swimming
```

```{r}
#| padding: 0px
#| title: "Time"
plot_time_swimming
```

```{r}
#| padding: 0px
#| title: "Pace"
plot_pace_swimming
```

```{r}
#| padding: 0px
#| title: "HR"
plot_hr_swimming
```

### Column {width="42.5%"}

#### Row {height="25%"}

##### Column {.tabset title="Cumulative"}

```{r}
#| padding: 0px
#| title: "Distance"
plot_cum_distance_swimming
```

```{r}
#| padding: 0px
#| title: "Time"
plot_cum_time_swimming
```

#### Row {height="75%"}

##### Column {.tabset title="Maps"}

```{r}
#| title: "Latest"
#| padding: 0px 
plot_map1_swimming
```

```{r}
#| title: "Fastest"
#| padding: 0px 
plot_map2_swimming
```

```{r}
#| title: "Longest"
#| padding: 0px 
plot_map3_swimming
```

```{r}
#| title: "All"
#| padding: 0px 
plot_map3_swimming
```
